Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-07-28 pirouette_article.tex
Fix figures, thanks @rsetienne
Addressed all feedback, thanks @rsetienne, fix #105

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_30/example_30_314/true_tree.png}
  \caption{
    The example tree resulting from a diversity-dependent (DD) simulation.
  }
  \label{fig:dd_tree}
\end{figure}

@@

The candidate model that had highest evidence given the simulated alignment,
was JC69, RLN and Yule (see Table \ref{tab:options} for the meaning of these 
abbreviations). JC69 was indeed the site model used when simulating the
alignments. The RLN clock model is a surprising result: it assumes that mutation rates differ between lineages, whereas the
alignment was simulated with equal mutation rates for all lineages \new{(strict clock)}.
\new{The Yule model is not surprising as it is the standard tree prior that is probably closest to the true DD model because it shows no pull-of-the-present (but also no slowdown).}

>>>>

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_30/example_30/true_tree.png}
  \caption{
    The example tree resulting from a diversity-dependent (DD) simulation.
  }
  \label{fig:dd_tree}
\end{figure}

@@

The candidate model that had highest evidence given the simulated alignment,
was TN, strict and BD (see Table \ref{tab:options} for the meaning of these 
abbreviations). 
The TN site model is a surprising result: it assumes nucleotide substitutions 
occur at different rates between translations and transversions 
and that nucleotides are available with different frequencies (that is,
a nucleotide may be rare or overabundant).
The strict clock model matches the model how the alignment is simulated.
\new{
  The Yule model is not surprising as it is the standard tree prior 
  that is probably closest to the true DD model because it shows 
  no pull-of-the-present (but also no slowdown).
}
